Semi-inclusive deep-inelastic scattering in Wandzura--Wilczek-type approximation

### 2019-05-29 arxiv2/test-WW-type-v2H.tex
AP

In this work, after introducing the SIDIS process and defining TMDs and
FFs (Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the WW(-type)
approximations, and review what is presently known about them
from experiment and theory (Sec.~\ref{Sec-3:WW}).
We will show that under the assumption of the validity of these approximations
all leading and subleading SIDIS structure functions are described in terms of
a basis of 6 TMDs and 2 FFs (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}),
and review how these basis functions describe available data
(Sec.~\ref{Sec-5:twist-2+basis}).
We will systematically apply the WW and/or WW-type approximations
to SIDIS structure functions at leading (Sec.~\ref{Sec-6:twist-2-and-WW})
and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist, and
conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).
The Appendices \ref{App:basis} and \ref{App:factor} contain
technical details.
An open-source package is available which allows one to visualize 
	and reproduce the results presented in this work, and may easily 
	be adapted by interested colleagues for their purposes
	\cite{Mathematica}.

\newpage
%======= SECTION 2: SIDIS & TMDs & FFs ===============================
\section{The SIDIS process in terms of TMDs and FFs}
\label{Sec-2:SIDIS+TMDs+FF}

@@

Experimental collaborations often define asymmetries in terms of counts
$N(\phi_h)$. This means the kinematic prefactors $p_i$ and $1/(x\,y\,Q^2)$
are included in the numerators or denominators of the asymmetries which
are averaged over $y$ within experimental kinematics. We will call the
corresponding asymmetries $\asympre{XY}{\rm weight}$.
For instance, in the unpolarized case one has
\be
	N(x,\dots,\phi) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
		+ \cos\phi\;\asympre{UU}{\cos\phi_h}(x,\dots)
		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
\ee
where $N_0$ denotes the total ($\phi_h$--averaged) number of counts
and the dots indicate further kinematic variables in the kinematic
bin of interest (which may also be averaged over).
It would be preferable if asymmetries were analyzed with known kinematic
prefactors divided out on event-by-event basis. One could then directly
compare asymmetries $\asym{XY}{\rm weight}$ measured in different
experiments and kinematics, and focus on effects of evolution
or power suppression for twist-3. In practice, often the kinematic
factors were included. We will define and comment on the explicit
expressions as needed.

For completeness we remark that after integrating the cross section
over transverse hadron momenta one obtains
\begin{subequations}\ba
     	\frac{d^4\sigma_{\rm leading}}{dx\,dy\,dz\,d\psi_l}
   &=&	 \frac{1}{2\pi}\;\frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z)
        \Biggl\{\;1 + \lambda\,S_L\,    p_2\,A_{LL} \Biggr\}
    	\label{Eq:SIDIS-leading-integrated} \\
	\frac{d^4\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l}
   &=&	 \frac{1}{2\pi}\;\frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z)
        \Biggl\{ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)}
  	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
          \Biggr\} \, ,
     \hspace{1cm} \label{Eq:SIDIS-subleading-integrated}
\ea\end{subequations}
where (and analogous for the other structure functions)
\be\label{Eq:FUU-integrated}
	F_{UU}(x,z) = \int d^2\Phperp\;F_{UU}(x,z,\Phperp)
\ee
and the asymmetries are defined as
\be
	A_{XY}^{\rm weight}(x,z) = \frac{F_{XY}^{\rm weight}(x,z)}{F_{UU}(x,z)}\,.
\ee

@@

\newpage
\begin{subequations}\ba
    \frac12\;{\rm Tr}\biggl[\gamma^+ \;\Phi(x)\biggr]
    &=& \hspace{5mm}
    \blue{f_1}\;, 	\label{Eq:pdf-I}\\
    \frac12\;{\rm Tr}\biggl[\gamma^+\gamma_5 \;\Phi(x)\biggr] &=&
    S_L\,\blue{g_1}\;, 	\label{Eq:pdf-II}\\
    \frac12\;{\rm Tr}\biggl[i\sigma^{j+}\gamma_5 \;\Phi(x)\biggr] &=&
    S_T^j\,\blue{h_1}\;, \label{Eq:pdf-III} \hspace{75mm}
\ea
and at twist-3 level
\ba
    \frac12\;{\rm Tr}\biggl[\,1\;\Phi(x)\biggr] &=&
    \frac{M_N}{P^+}\;\blue{e}\;,  \label{Eq:sub-pdf-I}\\
    \frac12\;{\rm Tr}\biggl[\gamma^j\gamma_5 \;\Phi(x)\biggr] &=&
    \frac{M_N}{P^+}\;S_T^j\,\blue{g_T} \;, \label{Eq:sub-pdf-II}\\ \hspace{6mm}
    \frac12\;{\rm Tr}\biggl[\,i\,\sigma^{+-}\gamma_5 \;\Phi(x)\biggr]
    &=& \frac{M_N}{P^+}\;S_L\,\blue{h_L}\,. \label{Eq:sub-pdf-III}\hspace{75mm}
\ea\end{subequations}
Other structures drop out either due to explicit $\kperp$--dependence,
or due to the sum rules \cite{Bacchetta:2006tn}
\be\label{Eq:sum-rules-T-odd}
	\int d^2\bfkperp\;f_T^a(x,\kperp^2)=
	\int d^2\bfkperp\;e_L^a(x,\kperp^2)=
	\int d^2\bfkperp\;h^a(x,\kperp^2)=0
\ee
imposed by time reversal constraints.

@@

\newpage

@@

In the T-even case one obtains the following approximations\footnote{%
	Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notation
	for transverse vectors, while in this paper we always utilize
	two-vectors for transverse vectors, such that e.g.\
	${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\mbox{\tiny Ref.~\cite{Bacchetta:2006tn}}}$
	and analog for other scalar products of {\it transverse} vectors.
	In our notation transverse vectors
	are never understood as four-vectors such that
	${\bfkperp^2}_{\rm our} \equiv {\kperp^2}_{\rm our}$.},
where the terms on the left-hand-side are twist-3, those on the
right-hand-side (if any) are twist-2,
\begin{subequations}\ba
xe^q(x,\kperp^2)	&\WWtype&
			0,
			\label{Eq:WW-type-1}\\
xf^{\perp q}(x,\kperp^2)  &\WWtype&
			f_{1}^q(x,\kperp^2),
			\label{Eq:WW-type-Cahn}\phantom{\frac11}\\
xg_L^{\perp q}(x,\kperp^2)&\WWtype&
			g_{1}^q(x,\kperp^2),
			\label{Eq:WW-type-gLperp}\phantom{\frac11}\\
xg_T^{\perp q}(x,\kperp^2)&\WWtype&
			g_{1T}^{\perp q}(x,\kperp^2),\phantom{\frac11}
			\label{Eq:WW-type-gTperp}\\
xg_T^q(x,\kperp^2)   	&\WWtype&
             		g_{1T}^{\perp(1)q}(x,\kperp^2),
			\label{Eq:WW-type-gT}\\
xh_L^q(x,\kperp^2)	&\WWtype& -2 \,
                       	h_{1L}^{\perp(1)q}(x,\kperp^2),\phantom{\frac11}
                       	\label{Eq:WW-type-6}\\
xh_T^q(x,\kperp^2)      &\WWtype&
                       	- h_1^q(x,\kperp^2) - h_{1T}^{\perp(1)}(x,\kperp^2),
                       	\label{Eq:WW-type-7}\\
xh_T^{\perp q}(x,\kperp^2)&\WWtype&
                       	\phantom{-}h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2).
                       	\phantom{\frac11} \label{Eq:WW-type-8}
\ea\end{subequations}
In the T-odd case one obtains the approximations
\begin{subequations}\ba
xe_L^q(x,\kperp^2)         	&\WWtype& 0,
			\label{Eq:WW-type-eLperp}\\
xe_T^q(x,\kperp^2)         	&\WWtype& 0, \\
xe_T^{\perp q}(x,\kperp^2) 	&\WWtype& 0, \\
xg^{\perp q}(x,\kperp^2)   	&\WWtype& 0,
                       	\label{Eq:WW-type-gperp}\\
xf_L^{\perp q}(x,\kperp^2) 	&\WWtype& 0,
			\label{Eq:WW-type-fLperp}\phantom{\frac11}\\
xf_T^{\perp q}(x,\kperp^2) 	&\WWtype&
                       	\phantom{-}\,f_{1T}^{\perp q}(x,\kperp^2),
			\phantom{\frac11}
                       	\label{Eq:WW-type-fTperp}\\
xf_T^{q}(x,\kperp^2)       	&\WWtype&
                       	-\,f_{1T}^{\perp(1)q}(x,\kperp^2), \label{Eq:WW-type-fT}\\
xh^q(x,\kperp^2)           	&\WWtype&
                       	- 2\,{h_1^{\perp(1)}(x,\kperp^2)}.\phantom{\frac11 XXXXx}
                       	\label{Eq:WW-type-last}
\ea\end{subequations}
The superscript ``(1)'' denotes the first transverse
moment of TMDs defined generically as
\ba
f^{(1)}(x,\kperp^2) = \frac{\kperp^2}{2M^2}\,f(x, \kperp^2)\; , \;\;\;
f^{(1)}(x ) = \int d^2 \kperp f^{(1)}(x,\kperp^2) \; .
\ea

@@

Does it mean WW-type approximations fail for $f_T^a(x,k_\perp^{2})$
and $h^a(x,k_\perp^{2})$? Not necessarily! The approximations may
work in some but not all regions of $\kperp$, but the sum rules
(\ref{Eq:sum-rules-T-odd}) include integration over all $k_\perp$.
Notice also that, e.g., $f_{1T}^{\perp (1),q}(x)$ is related to the
soft-gluon-pole matrix element $F_{FT}(x,x)$ \cite{Boer:2003cm,Ji:2006ub},
which is a $\bar{q}gq$-term that one would naturally neglect
in WW-type approximation.
In this sense (\ref{Eq:WW-type-fT}) could be consistent.
Thus, issues with the sum rules
(\ref{Eq:sum-rules-T-odd}) do not need to exclude the
possibility that the WW-type approximations for $f_T^a(x,k_\perp^{2})$ and
$h^a(x,k_\perp^{2})$ in (\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-last})
may work at small $k_\perp$ where we use them in our TMD approach.
This would mean that the UV region is essential to realize the sum rules
(\ref{Eq:sum-rules-T-odd}). Alternatively, one could also envision
the sum rules (\ref{Eq:sum-rules-T-odd}) to be sensitive to the
IR region through gluonic or fermionic pole contributions manifest
in tilde-terms.
Presently too little is known in the theory of subleading-twist TMDs.
In Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} we
will present pragmatic solutions for how to deal with the TMDs
$f_T^a(x,k_\perp^{2})$ and $h^a(x,k_\perp)$ phenomenologically.
For now let us keep in mind that
one has to keep a vigilant eye on all WW-type approximations, and
especially on those for $f_T^a(x,k_\perp^{2})$ and $h^a(x,k_\perp^{2})$.

@@

To conclude, the WW-type approximation predicts $A_{LU}^{\sin\phi}\approx 0$
in contradiction to experiment. The size of the observed effect seems
in line with the WW-type approximation, as
$A_{LU}^{\sin\phi_h}\sim\la\bar{q}gq\ra/\la\bar{q}q\ra \sim {\cal O}(2\,\%)$
is not large, although this interpretation has reservations.
$F_{LU}^{\sin\phi}$ is the only twist-3 SIDIS structure function not
``contaminated'' by leading twist. Attempts to describe this observable
and relevant model studies have been reported
\cite{Efremov:2002qh,Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej,
Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2013waa,Mao:2014dva,Lorce:2014hxa,Courtoy:2014ixa,Yang:2016mxl}.
But more phenomenological work and dedicated studies on the basis of models
of $\bar{q}gq$ terms are needed to fully understand this asymmetry.

@@

\section{Acknowledgments}
First and foremost, the authors would like to thank their families
for patience and constant support throughout writing this paper.
The authors would like to thank Werner Vogelsang for many useful
discussions. This work was partially supported by the U.S.\
Department of Energy under Contract No.~DE-AC05-06OR23177 (A.P.)
and within the TMD Collaboration framework, and by the National
Science Foundation under Contract No.\ PHY-1623454 (A.P.) and
Contract No.\ PHY-1406298 (P.S.), and the Wilhelm Schuler Stiftung (P.S.).
We thank the COMPASS and HERMES Collaborations for the 
permissions to show their preliminary data on several figures.

@@

The Boer--Mulders function $h_{1}^{\perp}$~\cite{Boer:1997nt} measures
the transverse polarization asymmetry of quarks inside an unpolarized
nucleon. The Boer--Mulders functions were studied phenomenologically in
Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}

>>>>

In this work, after introducing the SIDIS process and defining TMDs and
FFs (Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the WW(-type)
approximations, and review what is presently known about them
from experiment and theory (Sec.~\ref{Sec-3:WW}).
We will show that under the assumption of the validity of these approximations
all leading and subleading SIDIS structure functions are described in terms of
a basis of 6 TMDs and 2 FFs (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}),
and review how these basis functions describe available data
(Sec.~\ref{Sec-5:twist-2+basis}).
We will systematically apply the WW and/or WW-type approximations
to SIDIS structure functions at leading (Sec.~\ref{Sec-6:twist-2-and-WW})
and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist, and
conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).
The Appendices \ref{App:basis} and \ref{App:factor} contain
technical details.
An open-source package is available which allows one to visualize 
	and reproduce the results presented in this work, and may easily 
	be adapted by interested colleagues for their purposes~\footnote{Open-source packages with implementations of SIDIS structure functions
in the WW-type approximation are publicly available on github.com: in
Mathematica, Version 11.3 on https://github.com/prokudin/WW-SIDIS, in Python on https://jeffersonlab.github.io/jam3d.}.

%\newpage
%======= SECTION 2: SIDIS & TMDs & FFs ===============================
\section{The SIDIS process in terms of TMDs and FFs}
\label{Sec-2:SIDIS+TMDs+FF}

@@

Experimental collaborations often define asymmetries in terms of counts
$N(\phi_h)$. This means the kinematic prefactors $p_i$ and $1/(x\,y\,Q^2)$
are included in the numerators or denominators of the asymmetries which
are averaged over $y$ within experimental kinematics. We will call the
corresponding asymmetries $\asympre{XY}{\rm weight}$.
For instance, in the unpolarized case one has
\be
	N(x,\dots,\phi_h) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
		+ \cos\phi_h\;\asympre{UU}{\cos\phi_h}(x,\dots)
		+ \cos2\phi_h\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
\ee
where $N_0$ denotes the total ($\phi_h$--averaged) number of counts
and the dots indicate further kinematic variables in the kinematic
bin of interest (which may also be averaged over).
It would be preferable if asymmetries were analyzed with known kinematic
prefactors divided out on event-by-event basis. One could then directly
compare asymmetries $\asym{XY}{\rm weight}$ measured in different
experiments and kinematics, and focus on effects of evolution
or power suppression for twist-3. In practice, often the kinematic
factors were included. We will define and comment on the explicit
expressions as needed.

For completeness we remark that after integrating the cross section
over transverse hadron momenta one obtains
\begin{subequations}\ba
     	\frac{d^4\sigma_{\rm leading}}{dx\,dy\,dz\,d\psi_l}
   &=&	 \frac{1}{2\pi}\; \frac{4\pi \alpha_{em}^2}{xyQ^2}\biggl(1-y+\frac12y^2\biggr) \; F_{UU}(x,z)
        \Biggl\{\;1 + \lambda\,S_L\,    p_2\,A_{LL} \Biggr\}
    	\label{Eq:SIDIS-leading-integrated} \\
	\frac{d^4\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l}
   &=&	 \frac{1}{2\pi}\; \frac{4\pi \alpha_{em}^2}{xyQ^2}\biggl(1-y+\frac12y^2\biggr) \; F_{UU}(x,z)
        \Biggl\{ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} +
  \nonumber \\
  & &	 \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
          \Biggr\} \, ,
     \hspace{1cm} \label{Eq:SIDIS-subleading-integrated}
\ea\end{subequations}
where (and analogous for the other structure functions)
\be\label{Eq:FUU-integrated}
	F_{UU}(x,z) = \int d^2\Phperp\;F_{UU}(x,z,\Phperp)
\ee
and the asymmetries are defined as
\be
	A_{XY}^{\rm weight}(x,z) = \frac{F_{XY}^{\rm weight}(x,z)}{F_{UU}(x,z)}\,.
\ee

@@

%\newpage
\begin{subequations}\ba
    \frac12\;{\rm Tr}\biggl[\gamma^+ \;\Phi(x)\biggr]
    &=& \hspace{5mm}
    \blue{f_1}\;, 	\label{Eq:pdf-I}\\
    \frac12\;{\rm Tr}\biggl[\gamma^+\gamma_5 \;\Phi(x)\biggr] &=&
    S_L\,\blue{g_1}\;, 	\label{Eq:pdf-II}\\
    \frac12\;{\rm Tr}\biggl[i\sigma^{j+}\gamma_5 \;\Phi(x)\biggr] &=&
    S_T^j\,\blue{h_1}\;, \label{Eq:pdf-III} \hspace{75mm}
\ea
and at twist-3 level
\ba
    \frac12\;{\rm Tr}\biggl[\,1\;\Phi(x)\biggr] &=&
    \frac{M_N}{P^+}\;\blue{e}\;,  \label{Eq:sub-pdf-I}\\
    \frac12\;{\rm Tr}\biggl[\gamma^j\gamma_5 \;\Phi(x)\biggr] &=&
    \frac{M_N}{P^+}\;S_T^j\,\blue{g_T} \;, \label{Eq:sub-pdf-II}\\ \hspace{6mm}
    \frac12\;{\rm Tr}\biggl[\,i\,\sigma^{+-}\gamma_5 \;\Phi(x)\biggr]
    &=& \frac{M_N}{P^+}\;S_L\,\blue{h_L}\,. \label{Eq:sub-pdf-III}\hspace{75mm}
\ea\end{subequations}
Other structures drop out either due to explicit $\kperp$--dependence,
or due to the sum rules \cite{Bacchetta:2006tn}
\be\label{Eq:sum-rules-T-odd}
	\int d^2\bfkperp\;f_T^a(x,\kperp^2)=
	\int d^2\bfkperp\;e_L^a(x,\kperp^2)=
	\int d^2\bfkperp\;h^a(x,\kperp^2)=0
\ee
imposed by time reversal constraints.

@@

@@

In the T-even case one obtains the following approximations\footnote{%
	Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notation
	for transverse vectors, while in this paper we always utilize
	two-vectors for transverse vectors, such that e.g.\
	${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\mbox{\tiny Ref.~\cite{Bacchetta:2006tn}}}$
	and analog for other scalar products of {\it transverse} vectors.
	In our notation transverse vectors
	are never understood as four-vectors such that
	${\bfkperp^2}_{\rm our} \equiv {\kperp^2}_{\rm our}$.},
where the terms on the left-hand-side are twist-3, those on the
right-hand-side (if any) are twist-2,
\begin{subequations}\ba
xe^q(x,\kperp^2)	&\WWtype&
			0,
			\label{Eq:WW-type-1}\\
xf^{\perp q}(x,\kperp^2)  &\WWtype&
			f_{1}^q(x,\kperp^2),
			\label{Eq:WW-type-Cahn}\phantom{\frac11}\\
xg_L^{\perp q}(x,\kperp^2)&\WWtype&
			g_{1}^q(x,\kperp^2),
			\label{Eq:WW-type-gLperp}\phantom{\frac11}\\
xg_T^{\perp q}(x,\kperp^2)&\WWtype&
			g_{1T}^{\perp q}(x,\kperp^2),\phantom{\frac11}
			\label{Eq:WW-type-gTperp}\\
xg_T^q(x,\kperp^2)   	&\WWtype&
             		g_{1T}^{\perp(1)q}(x,\kperp^2),
			\label{Eq:WW-type-gT}\\
xh_L^q(x,\kperp^2)	&\WWtype& -2 \,
                       	h_{1L}^{\perp(1)q}(x,\kperp^2),\phantom{\frac11}
                       	\label{Eq:WW-type-6}\\
xh_T^q(x,\kperp^2)      &\WWtype&
                       	- h_1^q(x,\kperp^2) - h_{1T}^{\perp(1)q}(x,\kperp^2),
                       	\label{Eq:WW-type-7}\\
xh_T^{\perp q}(x,\kperp^2)&\WWtype&
                       	\phantom{-}h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)q}(x,\kperp^2).
                       	\phantom{\frac11} \label{Eq:WW-type-8}
\ea\end{subequations}
In the T-odd case one obtains the approximations
\begin{subequations}\ba
xe_L^q(x,\kperp^2)         	&\WWtype& 0,
			\label{Eq:WW-type-eLperp}\\
xe_T^q(x,\kperp^2)         	&\WWtype& 0, \\
xe_T^{\perp q}(x,\kperp^2) 	&\WWtype& 0, \\
xg^{\perp q}(x,\kperp^2)   	&\WWtype& 0,
                       	\label{Eq:WW-type-gperp}\\
xf_L^{\perp q}(x,\kperp^2) 	&\WWtype& 0,
			\label{Eq:WW-type-fLperp}\phantom{\frac11}\\
xf_T^{\perp q}(x,\kperp^2) 	&\WWtype&
                       	\phantom{-}\,f_{1T}^{\perp q}(x,\kperp^2),
			\phantom{\frac11}
                       	\label{Eq:WW-type-fTperp}\\
xf_T^{q}(x,\kperp^2)       	&\WWtype&
                       	-\,f_{1T}^{\perp(1)q}(x,\kperp^2), \label{Eq:WW-type-fT}\\
xh^q(x,\kperp^2)           	&\WWtype&
                       	- 2\,{h_1^{\perp(1)q}(x,\kperp^2)}.\phantom{\frac11 XXXXx}
                       	\label{Eq:WW-type-last}
\ea\end{subequations}
The superscript ``(1)'' denotes the first transverse
moment of TMDs defined generically as
\ba
f^{(1)}(x,\kperp^2) = \frac{\kperp^2}{2M^2}\,f(x, \kperp^2)\; , \;\;\;
f^{(1)}(x ) = \int d^2 \kperp f^{(1)}(x,\kperp^2) \; .
\ea

@@

Does it mean WW-type approximations fail for $f_T^a(x,k_\perp^{2})$
and $h^a(x,k_\perp^{2})$? Not necessarily! The approximations may
work in some but not all regions of $\kperp$, but the sum rules
(\ref{Eq:sum-rules-T-odd}) include integration over all $k_\perp$.
Notice also that, e.g., $f_{1T}^{\perp (1),q}(x)$ is related to the
soft-gluon-pole matrix element $F_{FT}(x,x)$ \cite{Boer:2003cm,Ji:2006ub},
which is a $\bar{q}gq$-term that one would naturally neglect
in WW-type approximation.
In this sense (\ref{Eq:WW-type-fT}) could be consistent.
Thus, issues with the sum rules
(\ref{Eq:sum-rules-T-odd}) do not need to exclude the
possibility that the WW-type approximations for $f_T^a(x,k_\perp^{2})$ and
$h^a(x,k_\perp^{2})$ in (\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-last})
may work at small $k_\perp$ where we use them in our TMD approach.
This would mean that the UV region is essential to realize the sum rules
(\ref{Eq:sum-rules-T-odd}). Alternatively, one could also envision
the sum rules (\ref{Eq:sum-rules-T-odd}) to be sensitive to the
IR region through gluonic or fermionic pole contributions manifest
in tilde-terms.
Presently too little is known in the theory of subleading-twist TMDs.
In Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} we
will present pragmatic solutions for how to deal with the TMDs
$f_T^a(x,k_\perp^{2})$ and $h^a(x,k_\perp^2)$ phenomenologically.
For now let us keep in mind that
one has to keep a vigilant eye on all WW-type approximations, and
especially on those for $f_T^a(x,k_\perp^{2})$ and $h^a(x,k_\perp^{2})$.

@@

To conclude, the WW-type approximation predicts $A_{LU}^{\sin\phi}\approx 0$
in contradiction to experiment. The size of the observed effect seems
in line with the WW-type approximation, as
$A_{LU}^{\sin\phi_h}\sim\la\bar{q}gq\ra/\la\bar{q}q\ra \sim {\cal O}(2\,\%)$
is not large, although this interpretation has reservations.
$F_{LU}^{\sin\phi}$ is the only twist-3 SIDIS structure function not
``contaminated'' by leading twist. Attempts to describe this observable
and relevant model studies have been reported
\cite{Efremov:2002qh,Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej,
Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2013waa,Mao:2014dva,Lorce:2014hxa,Courtoy:2014ixa,Yang:2016mxl, Pasquini:2018oyz}.
But more phenomenological work and dedicated studies on the basis of models
of $\bar{q}gq$ terms are needed to fully understand this asymmetry.

@@

\section{Acknowledgments}
First and foremost, the authors would like to thank their families
for patience and constant support throughout writing this paper.
The authors would like to thank Werner Vogelsang for many useful
discussions. This work was partially supported by the U.S.\
Department of Energy under Contract No.~DE-AC05-06OR23177 (A.P.)
and within the TMD Collaboration framework, and by the National
Science Foundation under Contract No.\ PHY-1623454 (A.P.) and
Contract No.\ PHY-1812423 (P.S.), and the Wilhelm Schuler Stiftung (P.S.). The work was supported by DOE grant no. DE-FG02-04ER41309.
We thank the COMPASS and HERMES Collaborations for the 
permissions to show their preliminary data on several figures.

@@

The Boer--Mulders function $h_{1}^{\perp}$~\cite{Boer:1997nt} measures
the transverse polarization asymmetry of quarks inside an unpolarized
nucleon. The Boer--Mulders functions were studied phenomenologically in
Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa},  we present the parameters of extractions of 
the Boer-Mulders frunction from Ref.~\cite{Barone:2010gk} in Tablel~\ref{fitparbm}.
